---
title: "EV Power - Renewable Energy by State"
format: typst
---

# Example Solution 1

## **Part 0: libraries**

```{r}
library(tidyverse)


```
## **Part 1:** **Overview**

Chosen Question: I wanted to understand the breakdown of renewable enrgy by state to see how it compares across the US. I decided to use the US total energy use dataset and create a map with states as the x-axis and renewable energy use as the y-axis, after filtering for just renewable energy.

## **Part 2: Description of Data and Methods **

I used pivot long to organize the data into a data frame with the columns being energy source, energy use, and states (see below for data and methods where I actually perform the pivot long).# 

## **Part 3: Data and Methods**

```{r}
library(tidyverse)

df <- read.csv("/Users/karuna/stat133/project_4/ev-power-karunaevach/data/total-use-2023.csv")

df_long <- df %>%
  pivot_longer(
    cols = -Energy_Source,        
    names_to = "State",           
    values_to = "Energy_Use"       
  )
  df_long
```

## **Part 4: Mapping Visualization**

```{r}
df_long |> filter(Energy_Source == "total renewable-energy") |> arrange(Energy_Use) |>
  ggplot(aes(y = Energy_Use,
             x = State, 
             group = State, color = State)) +
  geom_point() +
  geom_path() + scale_y_log10() + scale_y_discrete(expand = expansion(mult = c(1, 1))) +
  labs(title = "Renewable vs. Coal by state")
```
## **Part 5: Analysis**
I thought it was super interesting how most states seemed to have a relatively similar energy use. I would have expected the numbers to greatly differ, but they seemed quite consistent across the board. 